A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-08-28 paper/paper.tex
paper: typeset an array for iter param
paper: strip some useless minted stuff
paper: usepackage float for [H] specifier; not minted

\usepackage{multirow, minted, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape}
\usepackage[prefix=bonak]{art.cls/xkeymask}
\usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}

@@

% Code listings
\usemintedstyle{solarized-dark}
\setminted{escapeinside=~~}
\setmintedinline{escapeinside=~~}

@@

\subsection{Iterated parametricity}

>>>>

\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape}
\usepackage[prefix=bonak]{art.cls/xkeymask}
\usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}

@@

@@

\subsection{Iterated parametricity}
A full 2-cube is made of two full 1-cubes connected by a lifted 1-cube made of two lines connecting the former points and a square connecting the former lines:
\begin{equation*}
  \begin{array}{lll}
    \mbox{\textit{squares}}     \\
    [1mm]\mbox{\textit{lines}}  \\
    [1mm]\mbox{\textit{points}} \\
    [1mm]\end{array}
  \framebox{$\begin{array}{lll}
        \framebox{$
            \begin{array}{ll}
               & \framebox{$a_{0\star}$}              \\
              \framebox{$a_{00}$}~\framebox{$a_{01}$} \\
            \end{array}
          $}~
        \framebox{$
            \begin{array}{ll}
               & \framebox{$a_{1\unitpoint}$}         \\
              \framebox{$a_{10}$}~\framebox{$a_{11}$} \\
            \end{array}
          $}~
        \raisebox{4.8mm}{$\framebox{$
                \begin{array}{ll}
                   & \framebox{$a_{\unitpoint\unitpoint}$}                    \\
                  \framebox{$a_{\unitpoint 0}$}~\framebox{$a_{\unitpoint 1}$} \\
                \end{array}
              $}$}
      \end{array}$}
\end{equation*}
